% resume.tex
% vim:set ft=tex spell:

% Modified from http://www.toofishes.net/blog/latex-resume-follow-up/

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
%\usepackage{embedfile}

%for metadata
\usepackage[
            pdfauthor={Billy Rond},
            pdftitle={Resume/CV Billy Rond},
            pdfsubject={Resume/CV Billy Rond},
            pdfkeywords={Resume, Curriculum Vitae, CV, Billy Rond},
            pdfcreator={pdflatex, Via Github and Papeeria}]{hyperref}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
    {\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}
%\embedfile{resume.tex}
\begin{center}
{\LARGE \textbf{Billy C.\ Rond}}

1142 Westwood Road\ \ \textbullet
\ \ Bountiful, UT 84010
\\
(801) 915-6994\ \ \textbullet
\ \ billy.rond@gmail.com
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Department of Defense}}
		{\textbf{Hill Air Force Base, UT}}
	\\
	\headerrow
		{\emph{Systems Engineer}}
		{\emph{2009 -- Present}}
	\begin{itemize*}
                \item Part of a team responsible for
                        SLCM (software lifecycle management) of F-22 software. 
                        Provide Engineering support of various depot activations including F-22 SMS (stores management system),
                        radar, and power supply's.
                        Also Responsible for providing Diminished Manufacturing
                        Services (DMS) engineering oversight ensuring that the
                        F-22 systems stay operable.
                \item Provided SPO (systems program office) systems engineering support of aircraft simulators.
                        Coordinated the maintenance and CLS (Contract Logistics Support) for these simulators.
                        Supervise acquisition of systems for the upgrade of legacy simulator systems due to
                        training requirements and/or obsolescence. Oversee the testing of new systems to ensure
                        that they meet standards and integrate with existing systems. Due to restructuring of the
                        Air Force the Simulator SPO was moved to another base.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{L3 Communications Systems West}}
                {\textbf{Salt Lake City, UT}}
	\\
	\headerrow
		{\emph{Intern, Radio Frequency design group}}
		{\emph{Summer 2008}}
	\begin{itemize*}
                \item Summer Intern with L3 communications. Responsibilities at L3 included developing
                        new software that increased productivity. These programs interfaced over GPIB with
                        existing test equipment performing automated test procedures. These tests logged data
                        that was used to generate real-time graphs displaying part characteristics. Part of a team
                        designing a working prototype for government demonstrations. Worked for the RF
                        design team.
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{University of Utah}}
		{\textbf{Salt Lake City, UT}}
	\\
	\headerrow
		{\emph{College of Engineering, M.S. Electrical Engineering}}
		{\emph{2010-2011}}
	\begin{itemize*}
                \item Leader of a 5 person graduate/undergraduate diverse background engineering team at the
                        University of Utah. Team analyzed market feasibilities and developed an entrepreneurial
                        strategy for entrance into the market as well as a short term/long term strategy.
                        Responsible for delegating roles and integrating all the efforts of the team members in
                        developing these plans. Teams competed and were judged by each other and our team
                        finished among the top of our class.
	\end{itemize*}

\end{itemize}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{Utah State University}}
		{\textbf{Logan, UT}}
	\\
	\headerrow
		{\emph{College of Engineering, B.S. Electrical Engineering}}
		{\emph{2002 -- 2003,2005 -- 2009}}
	\begin{itemize*}
                \item Leader of a group that developed a biomimetic robotic beetle that mimicked the bouncing
                        motion of insects. This project required skills in both mechanic hardware and electrical
                        hardware interactions.
                \item Wrote proposal and entered senior design in the Utah State Entrepreneurial Contest.
                        Design and plan was chosen as one of top ten to be presented to three judges. Honored at
                        awards dinner.
	\end{itemize*}

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Core Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Software:]
	C, \CPP, ASM, Python, Verilog HDL, Linux, Windows, Labview, Matlab, MS office 
	\item[Hardware:]
	Microprocessors, Embedded Firmware, VLSI design, FPGA/PLC design, RF design
\end{description*}
\end{indentsection}

\hrule
\vspace{-0.4em}
\subsection*{Other}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{Voluntary Service}}
		{\textbf{Atlanta, GA}}
	\\
	\headerrow
		{\emph{Church Missionary}}
		{\emph{2003-2005}}
        \item Interests

        \begin{itemize*}
                \item Amateur radio operator (KE7OHB), have communicated with others all over the US.
                \item Sous-Vide, a PID controlled water oven for cooking food.
        \end{itemize*}

\end{itemize}

\end{document}
